---
title: "MADRID GROUP"
author: "BUSINESS TRAVEL"
date: '28&30 September, 2019'
output:
 
  html_document:
    css: FORMATO.css
    highlight: textmate
    theme: cosmo
    toc: yes
    toc_float: yes
---

<script> 
    $(document).ready(function() { 
    $head = $('#header'); 
    $head.prepend('<A href = https://www.cuttingedge-events.com><img src ="LOGO.png" width="150" vspace="50" align="right"></A>') 
    }); 
</script> 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```


```{r libraries}
library(readxl)
library(dplyr)
library(knitr)
library(timevis)

```


## Suggested Restaurants

### September 28th {.tabset .tabset-fade .tabset-pills}

#### Main option: Cafe Gijon

<iframe src="CAFE GIJON/CafeGijon.html" frameborder="0" width="100%" height="900" scrolling="no"></iframe>


**Basic Menu**

    Aperitive
    Oxtail croquettes

    Starters to choose (in advance)
    Albahaca salmorejo with tuna sashimi
    or
    Clams spanish style
    or
    Duck lasagna (with orange)
    or
    Tagliatelle salad with allioli, peppers and tuna.

    Main course to choose (in advance)
    Seafood-stuffed hake 
    or
    Iberica prey strips (Iberian pork)
    or
    Cordon-blue escalope

    Dessert
    White chocolate Pannacotta 

    Drinks
    Red or white wine (1 bottle each 3 pax) and water.

    *Rates per person: 40€ VAT inc
    + 3€ if you want to add coffee

<br>

#### Alternative: La Mucca de Serrano

<iframe src="LAMUCCA DE SERRANO/LaMuccadeSerrano.html" frameborder="0" width="100%" height="700" scrolling="no"></iframe>


**Basic Menu**

    To Share menu 

    - New Pisco
    - Spanish potatoes
    - Homemade croquettes
    - Nachos Teki
    - Green salad
    - Boletus pizza
    - Curry chicken
    - Fish and chips

    Desserts

    - Assortment of desserts

    Drinks

    - Red or white wine (1 bottle each 3 pax), water and coffee.
    They can change wine per beer or soft drinks ( 1 bittle of wine = 2l beer or 4 soft drinks)

    *Rates per person: 40€ VAT inc

<br>

### September 30th {.tabset .tabset-fade .tabset-pills}

#### Main option: Sinsombrero 

<iframe src="SINSOMBRERO/Sinsombrero.html" frameborder="0" width="100%" height="1000" scrolling="no"></iframe>


**Basic Menu**

    Starters to shre
    Russian salad with tuna
    Iberic ham croquettes
    Special pizza of picanha, red pesto, arugula and stracciatela.

    Main course to choose
    Roasted salmon with miso
    or
    Ox burguer with cheese and glazed shallots

    Dessert
    Chocolate cke with maracuya soup, crunchy honey and cookie ice cream.

    *Rates per person: 37€ VAT inc
     + 3€ if you want to add coffee

    Drink package option 1 - 12€

    - 3 drinks (glass of wine, beer, water or soft drink)

    Drink package option2 - 20€

    - 2h open bar (wine, beer, juices, water and soft drinks)



#### Alternative: Sagardi Castellana

<iframe src="SAGARDI CASTELLANA/SagardiCastellana.html" frameborder="0" width="100%" height="1000" scrolling="no"></iframe>


**Basic Menu**

    8 pintxos + 2 drinks (2 glasses of wine or 2 beers or 2 soft drinks) + 2 sweets (per person)

    *Pintxos to be chosen in advance*

    *Rates per person: 34€ VAT inc
    + 3€ if you want to add coffee


<br>

## Map

<iframe src="https://www.google.com/maps/d/u/0/embed?mid=1FVfAQOfiSzfr3g3ijd_Di5xwdRjHeopy" width="640" height="480"></iframe>

*****

## Terms & Conditions

  * Rates valid for 2019.
  
  * Net rates for Business travel
  
  * Cutting Edge Events management fee including in the detailed rates
  
  * VAT included. 
  
  * No reservation has been done. Availability upon request.
  
*****





