---
title: "MADRID GROUP"
author: "BUSINESS TRAVEL"
date: '28 September, 2019'
output:
 
  html_document:
    css: FORMATO.css
    highlight: textmate
    theme: cosmo
    toc: yes
    toc_float: yes
---

<script> 
    $(document).ready(function() { 
    $head = $('#header'); 
    $head.prepend('<A href = https://www.cuttingedge-events.com><img src ="LOGO.png" width="150" vspace="50" align="right"></A>') 
    }); 
</script> 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```


```{r libraries}
library(readxl)
library(dplyr)
library(knitr)
library(timevis)

```


## Suggested Restaurants

### September 28th {.tabset .tabset-fade .tabset-pills}

#### Main option: Cafe Gijon

<iframe src="CAFE GIJON/CafeGijon.html" frameborder="0" width="100%" height="900" scrolling="no"></iframe>


**Basic Menu**

*Aperitive*

- Oxtail croquettes

<br>

*Starters to choose*

- Albahaca salmorejo with tuna sashimi

- Clams spanish style

- Duck lasagna (with orange)

- Tagliatelle salad with allioli, peppers and tuna.

<br>

*Main course to choose*

- Seafood-stuffed hake 

- Iberica prey strips (Iberian pork)

- Cordon-blue escalope

<br>

*Desert and coffee*

- White chocolate Pannacotta 

*Drinks*

- Red or white wine (1 bottle each 3 pax) and water.

**40€ per person**

+ 3€ if you want to add coffee

<br>

#### Alternative: La Mucca de Serrano

<iframe src="LAMUCCA DE SERRANO/LaMuccadeSerrano.html" frameborder="0" width="100%" height="700" scrolling="no"></iframe>


**Basic Menu**

*To Share menu*

- New Pisco
- Spanish potatoes
- Homemade croquettes
- Nachos Teki
- Green salad
- Boletus pizza
- Curry chicken
- Fish and chips

*Desserts*

- Assortment of desserts

*Drinks*

- Red or white wine (1 bottle each 3 pax), water and coffee.
They can change wine per beer or soft drinks ( 1 bittle of wine = 2l beer or 4 soft drinks)

**40€ per person**

<br>

### September 30th {.tabset .tabset-fade .tabset-pills}

#### Main option: Sinsombrero 

<iframe src="SINSOMBRERO/Sinsombrero.html" frameborder="0" width="100%" height="1000" scrolling="no"></iframe>


**Basic Menu**

*Starters* 

- Russian salad with tuna

- Iberic ham croquettes

- Special pizza of picanha, red pesto, arugula and stracciatela.

*Main course to choose*

- Roasted salmon with miso

- Ox burguer with cheese and glazed shallots

<br>

*Desert*

- Chocolate cke with maracuya soup, crunchy honey and cookie ice cream.

<br>

**37€ per person**

+ 3€ if you want to add coffee

**Drink package 1 - 12€**

- 3 drinks (glass of wine, beer, water or soft drink)

**Drink package 2 - 20€**

- 2h open bar (wine, beer, juices, water and soft drinks)



#### Alternative: Sagardi Castellana

<iframe src="SAGARDI CASTELLANA/SagardiCastellana.html" frameborder="0" width="100%" height="1000" scrolling="no"></iframe>


**Basic Menu**

8 pintxos + 2 drinks (2 glasses of wine or 2 beers or 2 soft drinks) + 2 sweets (per person)

*Pintxos to be chosen in advance*

**34€ per person**



<br>

## Map

<iframe src="https://www.google.com/maps/d/u/0/embed?mid=1FVfAQOfiSzfr3g3ijd_Di5xwdRjHeopy" width="640" height="480"></iframe>

*****

## Terms & Conditions

  * Rates valid for 2019.
  
  * Net rates for Business travel
  
  * Cutting Edge Events management fee including in the detailed rates
  
  * VAT included. 
  
  * No reservation has been done. Availability upon request.
  
*****





